DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-29 paper/intro.tex
still revising (unsatisfactory.)

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies for ever more autonomous decision making
capabilities---ultimately fully autonomous driving capability without
any human intervention. One of the key technologies for increased
autonomy of a vehicle is deep neural network (DNN) models, which have
been sucessfully applied in various perception and control tasks in
recent years. Already, DNN models are used in commercial
semi-autonomous vehicles such as Tesla Model S, which includes a poweful
computer and accelerators (e.g., MobileEye EyeQ) to execute various
DNN models, espeically for (vision-based) real-time perception
tasks. DNN based end-to-end control of a vehicle is also actively
explored in recent years~\cite{Bojarski2016}.

% requirements:
%   (1) real-time processing.
%   (2) cost
%   (3) safety
%   (4) SWaP
%
% our goals:
%   (1) build a safe and low cost testbed but utilizing the
%       state-of-the-art AI technologies: DNN based end-to-end control
%   (2) analyze real-time issues in DNN based end-to-end control.
%   (3) evalute popular embedded platforms for the AI workloads
%       (end-to-end control, perception).
%       - Can apsberry pi handle AI workloads?
%       - Can embedded GPU do better? How much?
There are several challenges in studying autonomous vehicles.

it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

>>>>

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies for ever more autonomous decision making
capabilities---ultimately fully autonomous driving capability without
any human intervention. Deep neural networks (DNNs) have been
sucessfully applied in various perception and control tasks in 
recent years, and they are important workloads for autonomous vehicles
as well. For example, Tesla Model S was known to use a specialized SoC
(MobileEye EyeQ), which uses a deep neural network for vision-based
real-time obstacle detection and avoidance. More recently, researchers
are investigating DNN based end-to-end control of
cars~\cite{Bojarski2016} and other robots. It is expected that more
DNNs based Artifical Intelligence workloads may be used in future
autonomous vehicles.

% need testbeds.
% but challenges 
%   (1) real-time processing (2) cost (3) safety (4) SWaP
Developing and testing DNN models for autonomous vehicles is
however, challenging for a variety of reasons. The first challegen is
finding a suitable computing platform. It is generally known that DNN
models are computationally demainding. Furtheremore, because many of
the AI workloads, such as models for end-to-end control or perception,
have strict real-time requirements as cars have to interact with the
physical world in real-time. On the other, the computing platform must
also satisfy cost, size, weight, and power constraints. 
The second challenge is preparing a
physical car platform to collect data and test the software. While
instrumenting a real-car would be most realistic, as many
companies such as google and uber are doing, but doing it is costly
and would pose safety concerns. 
% our goals:
%   (1) build a safe and low cost testbed but utilizing the
%       state-of-the-art AI technologies: DNN based end-to-end control
%   (2) analyze real-time issues in DNN based end-to-end control.
%   (3) evalute popular embedded platforms for the AI workloads
%       (end-to-end control, perception).
%       - Can apsberry pi handle AI workloads?
%       - Can embedded GPU do better? How much?
Therefore, there is a strong need for low-cost testbeds that still
employs state-of-the-art AI technologies and are capable of executing
real-time autonomous vehicle operations.

%% it is necessary that all real-time operations are successfully
%% performed prior to their deadlines. This requires that the AV platform
%% be capable of completing all necessary computations in a timely
%% manner, while maintaining a high level of accuracy. Consequently, the
%% cost of creating a platform capable of self-driving can be relatively
%% high, especially in the current cost-sensitive climate of the
%% automotive industry \cite{}. The overall price for an autonomous
%% vehicle platform currently acts as a bottleneck, especially from an
%% academic standpoint, where cost is an important factor. For many
%% researchers and students, the charge associated with autonomous
%% vehicle research is a significant barrier. These same parties may also
%% be deterred from participating in autonomous vehicle research due to
%% the potential for their developed platforms to break in the
%% experimental process. The idea of building one relatively expensive
%% platform may not be too daunting for some, but the notion of
%% potentially making multiple identical platforms in case of accidents
%% may be overwhelming.
%% Toward this end, we explore the possibility of
%% developing a low-cost system that still employs state-of-the-art AI
%% technologies and is capable of executing real-time autonomous vehicle
%% operations.
